%Document, Graphics, and Figures
\documentclass[12pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{images/}} %tells images where stored  

%Printing settings
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
%Headers and Footers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{Coverage Analysis in Fine Mapping Genetic Associations}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[LO,CE]{Chapter \thechapter}
\fancyfoot[CO,RE]{Hope M. Watson}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

%Bibliography
\usepackage{biblatex}
\bibliographystyle{unsrt}
\addbibresource{references.bib}

%Title Page
\title{Coverage Analysis in Fine Mapping Genetic Associations}
\author{Hope M. Watson }
\date{August 2018}

\begin{document}

\input{chapters/Titlepage.tex}

\chapter*{Abstract}


\chapter*{Acknowledgements}
I would like to thank the many people who made this thesis possible. Without their help I would not have grown as an academic and begin to change how I see phenomena occurring in the world. I especially like to thank Dr. Chris Wallace and Dr. Jennifer Asimit, for continuously helping me all throughout this thesis and assisting me in the many questions I asked. I would like to thank Dr. Deborah Thompson for helping edit this thesis and being a devoted supervisor and mentor during my entire year, both academically and personally. 
\chapter*{Dedication}
For my Dad. Without your love, support, and encouragement I wouldn't be half the person I am today.

\chapter*{Declaration}
I declare that this thesis is the result of my own work. All sources are fully acknowledged and
appropriately cited. The contents of this submission have not been used to any extent for a comparable
purpose, i.e., in partial fulfillment of another degree or diploma at any university or institute of
higher learning.

\tableofcontents 
\listoffigures

\chapter{Introduction}
\input{chapters/Introduction.tex}

\chapter{Background}
\input{chapters/Background.tex}

\chapter{Methods}
\input{chapters/Methods.tex}

\chapter{Results}
\input{chapters/Results.tex}

\chapter{Discussion}
\input{chapters/Discussion.tex}

\chapter{Conclusion}
\input{chapters/Conclusion.tex}

\appendix 
\chapter{Appendix}
\input{chapters/Appendix.tex}

\printbibliography


\end{document}
